SMT-COMP 20243\\ 19th International Satisfiability Modulo Theory Competition

### 2024-07-20 2024/slides/presresults/slides.tex
Updated slides for 2024

\begin{frame}[fragile]
  \frametitle{Plans for SMT-COMP 2025?}
  \begin{itemize}
    \item<1-> General: documentation and streamlining
    \item<2-> General: more CI support for submissions
    \item<3-> Cloud/Parallel: (re)gain more control
      \begin{itemize}
        \item<4-> long term guarantee that the tracks will be held
        \item<5-> more transparency
        \item<6-> better communication
      \end{itemize}
    \item<7-> Proof \textit{validation} track:
      \begin{itemize}
        \item<8-> we still have to analyze the data (830gb)
        \item<9-> ideas to turn this into a competition are welcome
      \end{itemize}
    \item<10-> Derived tools: how to determine their contribution compared to the tools they are derived from
      \begin{itemize}
        \item<11-> esp. competition wide scoring, e.g., biggest contribution
        \item<12-> potential solution: run the tools they are derived from non-competitively and disqualify from logics if there is not a sufficient amount of improvement
      \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}[fragile]
  \frametitle{SMT-COMP 2024: a year of changes}
  \begin{itemize}
    \item Switch from StarExec to BenchExec
    \begin{itemize}
	    \item A big thanks to Dirk Beyer and Philipp Wendler for offering us to use the VerifierCloud and their support   
        \item A big thanks to Aaron Stump for his StarExec support over the years
    \end{itemize}
    \item New submission process (pull requests)
    \item CI support for submissions
    \item Merge of all competition scripts into one tool
    \begin{itemize}
        \item enhancing their speed by orders of magnitude
    \end{itemize}
    \item New AWS team taking care of the cloud and parallel tracks
    \item Proof track discontinued (for now)
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Plans for SMT-COMP 2025}
  \begin{itemize}
    \item<1-> General: documentation and streamlining
    \item<2-> General: more CI support for submissions
    \item<3-> Cloud/Parallel: (re)gain more control
      \begin{itemize}
        \item<4-> long term guarantee that the tracks will be held
        \item<5-> more transparency
        \item<6-> better communication
      \end{itemize}
    \item<7-> Proof track:
      \begin{itemize}
        \item<8-> we still have to analyze the data (830gb)
        \item<9-> ideas to turn this into a competition are welcome
      \end{itemize}
    \item<10-> Derived tools: how to determine their contribution compared to the tools they are derived from
      \begin{itemize}
        \item<11-> esp. competition wide scoring, e.g., biggest contribution
        \item<12-> potential solution: run the tools they are derived from non-competitively and disqualify from logics if there is not a sufficient amount of improvement
      \end{itemize}
  \end{itemize}
\end{frame}
